### 2014-08-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Updates to ventilation timeline and details

\begin{table}[!ht]
\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
\begin{tabular}{cl}
\toprule
Incident Time  &  Fire Behavior / Fireground Operation                                                \\
{(hh:mm:ss)}   &                                                                                      \\
\midrule
10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
               &                                                                                      \\
10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
               &  the front door with a 1 3/4'' hoseline.                                             \\
               &                                                                                      \\
10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
               &                                                                                      \\
10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
               &                                                                                      \\
10:58:42       &  Fire self-vents from the rear side of the structure when a glass door in the        \\
               &  basement fails.                                                                     \\
               &                                                                                      \\
10:59:00       &  BC9 forces open the basement door on the left side of the structure,                \\
               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
               &                                                                                      \\
11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
               &                                                                                      \\
11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
               &                                                                                      \\
11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
               &  suppression operations.                                                             \\
               &                                                                                      \\
11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
               &                                                                                      \\
11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
               &                                                                                      \\
\bottomrule
\end{tabular}
\label{tab:incident_timeline}
\end{table}

@@

\begin{table}[!ht]
\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
\begin{tabular}{ccll}
\toprule
FDS Simulation  &  Ventilation  &  Type                &  Location of Vent        \\
Time            &  Area         &                      &                          \\
{(s)}           &  (m$^2$)      &                      &                          \\
\midrule
0               &  1.47         &  Door                &  Front Exterior          \\
0               &  1.68         &  Door                &  Interior (Stairwell)    \\
0               &  1.68         &  Door                &  Interior (Garage)       \\
0               &  10.1         &  Overhead Door       &  Front Exterior          \\
N/A$^*$         &  1.68         &  Door                &  Left Basement Exterior  \\
342             &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
383             &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
418             &  2.52         &  Window              &  Rear Basement Exterior  \\
440             &  2.31         &  Window              &  Rear Basement Exterior  \\
450             &  3.78         &  Sliding Glass Door  &  Rear Basement Exterior  \\
\bottomrule
\end{tabular}
\footnotesize
\\$^*$This ventilation event was not included in the simulation.
\normalsize
\label{tab:ventilation_timeline}
\end{table}

@@

10:58:42       &  342         &  Fire self-vents from the rear side of the structure when a       \\
               &              &  glass door in the basement fails.                                \\

@@

10:59:00       &  360         &  BC9 forces open the basement door on the left side of            \\

>>>>

\begin{table}[!ht]
\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
\begin{tabular}{cl}
\toprule
Incident Time  &  Fire Behavior / Fireground Operation                                                \\
{(hh:mm:ss)}   &                                                                                      \\
\midrule
10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
               &                                                                                      \\
10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
               &  the front door with a 1 3/4'' hoseline.                                             \\
               &                                                                                      \\
10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
               &                                                                                      \\
10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
               &                                                                                      \\
10:58:42       &  Fire self-vents from the rear side of the structure when a glass window in the      \\
               &  basement fails. Additional glass windows on the rear side of the structure fail     \\
               &  over the next two minutes.                                                          \\
               &                                                                                      \\
10:59:23       &  BC9 forces open the basement door on the left side of the structure,                \\
               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
               &                                                                                      \\
11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
               &                                                                                      \\
11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
               &                                                                                      \\
11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
               &  suppression operations.                                                             \\
               &                                                                                      \\
11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
               &                                                                                      \\
11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
               &                                                                                      \\
\bottomrule
\end{tabular}
\label{tab:incident_timeline}
\end{table}

@@

\begin{table}[!ht]
\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
\begin{tabular}{ccll}
\toprule
FDS Simulation Time  &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
{(s)}                &  (m$^2$)           &                      &                           \\
\midrule
0                    &  1.47              &  Door                &  Front Exterior           \\
0                    &  10.1              &  Overhead Door       &  Front Exterior (Garage)  \\
0                    &  1.68              &  Door                &  Interior (Stairwell)     \\
0                    &  1.68              &  Door                &  Interior (Garage)        \\
342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.68              &  Door                &  Left Basement Exterior   \\
418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
440                  &  2.31              &  Window              &  Rear Basement Exterior   \\
450                  &  3.78              &  Sliding Glass Door  &  Rear Basement Exterior   \\
\bottomrule
\end{tabular}
\label{tab:ventilation_timeline}
\end{table}

@@

10:58:42       &  342         &  Fire self-vents from the rear side of the structure when a glass  \\
               &              &  window in the basement fails. Additional glass windows on the     \\
               &              &  rear side of the structure fail over the next two minutes.        \\

@@

10:59:23       &  383         &  BC9 forces open the basement door on the left side of             \\
